A multiverse analysis of the associations between internet use and well-being

### 2022-12-16 ms.Rmd
:heart: renv

```{r}
#| label: setup
#| include: false
library(papaja)
library(scales)
library(knitr)
library(lme4)
library(ggh4x)
library(emmeans)
library(ggside)
library(ggbeeswarm)
library(broom.mixed)
library(patchwork)
library(ggdist)
library(corrr)
library(tidyverse)
opts_chunk$set(
  include = FALSE,
  cache = TRUE,
  dev = "ragg_png"
)

>>>>

```{r}
#| label: setup
#| include: false
library(papaja)
library(scales)
library(knitr)
library(lme4)
library(ggh4x)
library(emmeans)
library(ggside)
library(ggbeeswarm)
library(broom.mixed)
library(patchwork)
library(ggdist)
library(corrr)
library(tidyverse)
library(ragg)
opts_chunk$set(
  include = FALSE,
  cache = TRUE,
  dev = "ragg_png"
)
